Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})

### 2018-01-23 doc/tsl_amnat.tex
rejected from bjls. reformatted for peerj

\documentclass[12pt,letterpaper]{article}

\usepackage{amsmath, amsthm}
\usepackage{graphicx,hyperref}
\usepackage{microtype, parskip}
\usepackage{natbib}
\usepackage{lineno}
\usepackage[font=small]{caption}
\usepackage{float}
\usepackage{subcaption, multirow, morefloats}
\usepackage{, wrapfig}
\usepackage{afterpage}
\usepackage{rotating}
\usepackage{titlesec}
\usepackage[nottoc,numbib]{tocbibind}
\usepackage{authblk, attrib, fullpage}
\usepackage{lineno}

\frenchspacing

\captionsetup[subfigure]{position = top, labelfont = bf, textfont = normalfont, singlelinecheck = off, justification = raggedright}

\renewcommand{\section}[1]{%
\bigskip
\begin{center}
\begin{Large}
\normalfont\scshape #1
\medskip
\end{Large}
\end{center}}

\renewcommand{\subsection}[1]{%
\bigskip
\begin{center}
\begin{large}
\normalfont\itshape #1
\end{large}
\end{center}}

\renewcommand{\subsubsection}[1]{%
\vspace{2ex}
\noindent
\textit{#1.}---}

\renewcommand{\tableofcontents}{}

\bibpunct{(}{)}{;}{a}{}{,}  % this is a citation format command for natbib

%\title{How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in the Pacific Pond Turtle (\textit{Emys marmorata})}
\title{Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})}
\author[1]{Peter D Smits}%\thanks{peterdavidsmits@gmail.com}}
\author[2]{Kenneth D Angielczyk}%\thanks{kangielczyk@fieldmuseum.org}}
\author[3]{James F Parham}%\thanks{jparham@fullerton.edu}}
\author[4]{Bryan L Stuart}%\thanks{bryan.stuart@naturalsciences.org}}
\affil[1]{Department of Integrative Biology, University of California -- Berkeley}
\affil[2]{Integrative Research Center, Field Museum of Natural History}
\affil[3]{John D. Cooper Archaeological and Paleontological Center, Department of Geological Sciences, California State University, Fullerton}
\affil[4]{Section of Research and Collections, North Carolina Museum of Natural Sciences}

\begin{document}
\maketitle
\noindent{\textbf{Corresponding author:} Peter D Smits, Department of Integrative Biology, University of California -- Berkeley, 3040 Valley Life Sciences Building \#5151, Berkeley, CA, 94720, USA; E-mail: \href{mailto:psmits@berkeley.edu}{psmits@berkeley.edu}

\linenumbers
\modulolinenumbers[2]

\begin{abstract}

  We investigated the morphometric identification of cryptic species using machine learning approaches by examining their implications for a recently proposed cryptic turtle species (\textit{Emys pallida}). We collected landmark-based morphometric data from 532 adult \textit{E. marmorata/``E. pallida''} museum specimens. We assigned a classification to each specimen for six different binning schemes based on geographic occurrence data recorded in museum collection archives. We used an ensemble of supervised machine learning approaches to determine which classification hypothesis was best supported by the data. In addition, we applied the same approach to two clear-cut examples, one consisting of eight unambiguously distinct species closely related to \textit{E. marmorata}, and the other consisting of two subspecies of \textit{Trachemys scripta}. Our results indicate that there is no clear ``best'' grouping of \textit{E. marmorata/``E. pallida''} based on plastron shape. In contrast, the analyses of the clear-cut examples produced near perfect classifications, demonstrating that the methods can recover correct results when an appropriate signal exists. Explanations for the lack of grouping in \textit{E. marmorata} include the possibility that genetic differentiation is not associated with plastron shape variation below the species level and/or that local selective pressures (e.g., from hydrological regime) overwhelm morphological differentiation. A reconsideration of the methods used to delimit \textit{``E. pallida,''} the lack of barriers to gene flow, the strong evidence for widespread admixture between lineages, and the fact that plastron shape can be used to delineate other emydine species and sub-species suggest that its lack of diagnosability most likely reflects the non-distinctiveness of this proposed taxon. 
\end{abstract}

\section{Introduction}
% cryptic diversity
%   most species are still deliminated solely based on morphology
Molecular systematics has repeatedly demonstrated the existence of cryptic species that can only be diagnosed using genetic data \citep{Stuart2006,Bickford2007,SchlickSteiner2007,Pfenninger2007,Clare2011,Funk2012}. In attempts to streamline the documentation of biodiversity, several methods of species delimitation that rely almost entirely on genetic data have recently been proposed \citep{Pons2006,Carstens2010,Hausdorf2010,O'Meara2010,Yang2010b,Huelsenbeck2011b}. Although strong caveats on the utility of these methods have been raised \citep{Bauer2000,Carstens2013}, they are nevertheless being used to name species \citep{Leache2010,Spinks2014}.

@@

% past work on automatic taxon identification and older approaches to classifying taxa
% why use machine learning methods
\subsection{Background and study system}
Machine learning is an extension of known statistical methodology \citep{Hastie2009} that emphasizes predictive accuracy and generality often at the expense of the interpretability of individual parameters. Basic statistical approaches are supplemented by randomization, sorting, and partitioning algorithms, along with the maximization or minimization of summary statistics, in order to best estimate a general model for all data, both sampled and unsampled \citep{Hastie2009}. Machine learning approaches have found use in medical research, epidemiology, economics, and automated identification of images such as handwritten zip codes \citep{Hastie2009}. % additional/more specific CITATIONS?

@@

\section{Materials and Methods}
\subsection{Specimens, sampling, morphometrics}

\afterpage{\clearpage}
\begin{figure}[ht]
  \centering
  \includegraphics[height = 0.8\textheight, width = \textwidth, keepaspectratio = true]{figure/Ken_Ang_SpLoc_final_comp}
  \caption{Geographic distribution of specimens sampled for comparing the hypothesized subdivisions of \textit{Emys marmorata}. Each hypothesized scheme has two or more possible classes. Sample size differs between schemes because of our ability to confidently assign museum specimens to the various schemes. The number of localities shown on each map is less than the number of specimens sampled because some localities produced multiple specimens. The different classification abbreviations are as follows: \textit{E. marmorata} = ``marm'', \textit{E. pallida} = ``pall'', Central Coast Ranges = ``CCR'', San Joaquin Valley = ``SJ,'' Baya Peninsula = ``Baja,'', and Sierra Foothills = ``Foothill.''}
  \label{fig:map}
\end{figure}

\afterpage{\clearpage}
\begin{figure}[ht]
  \centering
  \includegraphics[height = 0.5\textheight, width = \textwidth, keepaspectratio = true]{figure/plastra}
  \caption{Depiction of general plastral shape of \textit{E. marmorata} and position of the 19 landmarks used in this study. Anterior is towards the top of the figure.}
  \label{fig:plastra}
\end{figure}

@@

\begin{table}
  \centering
    \caption{Table of species delimitation hypotheses for \textit{E. marmorata}}
    \begin{tabular}{l l l }
      \hline
      Abbreviation & Number of classes & citation \\
      \hline
      SP10.1 & 3 & \citet{Spinks2010} \\
      SP10.2 & 3 & \citet{Spinks2010} \\
      SP10.3 & 4 & \citet{Spinks2010} \\
      SP14.1 & 2 & \citet{Spinks2014} \\
      SP14.2 & 4 & \citet{Spinks2014} \\
      Morph & 2 & \citet{Spinks2010} \\
      \hline
    \end{tabular}
    \label{tab:hypotheses}
\end{table}

@@

\subsection{Biasing effects}
% digitization
We estimated the possible effect of digitization error \citep{Arnqvist1998,Cramon2007,Munoz-MunozF.2010} on our results by comparing within-specimen (replicated) Procrustes distances to the distances between classification scheme centroids. Ten randomly-selected \textit{E. marmorata} specimens were each digitized four times, with the original set of digitized coordinates serving as a fifth replicate. These 50 landmark configurations were then Procrustes superimposed. A range of four Procrustes distances was then calculated as the average of the pairwise distances between each of the replicate configurations of a given specimen.

@@

\subsection{Supervised learning approaches}

\begin{table}
  \centering
  \caption{Table of the supervised learning methods used in this analysis.}
  \scalebox{0.9}{
  \begin{tabular}{l l l l}
    \hline
    Method name & abbreviation & R package & citation \\
    \hline
    multinomial logistic regression & MLR & nnet & \citet{Venables2002} \\
    linear discriminate analysis & LDA & MASS & \citet{Venables2002} \\
    penalized discrminiate analysis & PDA & mda & \citet{mdapack} \\
    single-hidden-layer neural network & NN & nnet & \citet{Venables2002} \\
    random forests & RF & randomForest & \citet{Liaw2002} \\
    \hline
  \end{tabular}}
  \label{tab:methods}
\end{table}

@@

\section{Results}

\subsection{Geometric morphometrics}

\begin{figure}[h]
  \centering
  \begin{subfigure}[b]{0.7\textwidth}
    \caption{}
    \includegraphics[width = \textwidth]{figure/cc7_pc_graph}
  \end{subfigure}

  \begin{subfigure}[b]{0.7\textwidth}
    \caption{}
    \includegraphics[width = \textwidth]{figure/tra_pc_graph}
  \end{subfigure}
  \caption{Two scatterplots of morphological differences from two of the three datasets analyzed in this study. (a) Scatterplot of the first two PCA axies from the landmarks from the eight different species dataset, and (b) the first two axes of variation from two subspecies of \textit{Trachemys} dataset. Point colors correspond to the categories within each dataset while point size is proportional to individual centroid size. In parentheses next to the axis labels are the percent of total variation accounted for by that axis. For both datasets there are clear distinctions between the different categories.}
  \label{fig:other_pca}
\end{figure}

\afterpage{\clearpage}
\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/emys_pc_graph}
  \caption{Scatterplot of the first two axes of morphological variation in the \textit{Emys marmorata} dataset. Each panel corresponds to one of the six different classification schemes analyzed as part of this study (Tab. \ref{tab:hypotheses}). Point color corresponds to the categories within each scheme, and the class names correspond to geographic regions. Point size is proportional to centroid size of that specimen and the numbers in parentheses next to the axis labels are the percent of total variation accounted for along that axis.}
  \label{fig:emys_pca}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[height = 0.3\textheight, width = \textwidth, keepaspectratio = true]{figure/sex_test_hist}
  \caption{Comparison of observed Procrustes distance between the centroids of each sex (vertical line) to a null distribution generated from 1000 permutations of the sex-labels. This result indicates that the difference between the centroids is as small/smaller than expected by random.}
  \label{fig:sex_test}
\end{figure}

@@

\begin{table}
  \centering
  \caption{Results from the within-individual to between-individual Procrustes distances for the replicated plastron shape data. Results are presented for all three datasets analyzed here: the \textit{Trachemys} dataset, the eight species dataset, and each of the \textit{Emys marmorata} classification schemes.}
  \begin{tabular}{l l c c}
    \textbf{Dataset} & \textbf{Scheme} & \textbf{Ratio} & \textbf{Corrected ratio} \\
    \hline
    Replicates & & 1.11 & \\
    \hline
    Seven species & & 0.33 & 0.37 \\
    \textit{Trachemys} & & 0.76 & 0.84 \\
    \hline
    \textit{E. marmorata} & SP10.1 & 0.99 & 1.10 \\
     & SP10.2 & 1.00 & 1.11 \\
     & SP10.3 & 0.94 & 1.04 \\
     & SP14.1 & 1.01 & 1.12 \\
     & SP14.2 & 0.93 & 1.04 \\
     & Morph & 0.99 & 1.09 \\
    \hline
  \end{tabular}
  \label{tab:rep_res}
\end{table}

@@

\subsection{Supervised learning}

\begin{figure}[h]
  \centering
  \includegraphics[height = 0.5\textheight, width = \textwidth, keepaspectratio = true]{figure/other_model_sel}
  \caption{Comparisons of model fit to the training dataset for each of the supervised learning methods applied to the first two datasets; the results from the eight species dataset are presented in the left column, while those from the \textit{Trachemys} dataset are presented in the right column. Models were fit to datasets of varying complexity, with the number of parameters listed along the x-axis. Model fit is measured as the area under the receiver operating characteristic (AUC), which ranges from 0.5 to 1. Error bars correspond to one standard error estimated from 10 rounds of 5-fold cross-validation. The red dot corresponds to the model fit with the highest mean AUC while the blue dot corresponds to the model selected for further analysis. In some cases, there is no difference in complexity between the best and selected models.}
  \label{fig:other_sel}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[height = 0.3\textheight, width = \textwidth, keepaspectratio = true]{figure/other_oos_sel}
  \caption{The results of out-of-sample predictive performance of the selected models for both the eight species (left) and \textit{Trachemys} datasets. Predictive performance is measured as the area under the receiver operating characteristic (AUC), which ranges from 0.5 to 1. Points correspond to the individual out-of-sample predictive performance of the specific model, indicated along the x-axis. The horizontal bars correspond the average out-of-sample predictive performance of all the models.}
  \label{fig:other_oos}
\end{figure}

@@

\afterpage{\clearpage}
\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/emys_model_sel}
  \caption{AUC values for models of varying complexity fit to the \textit{Emys marmorata} training datasets for each classification scheme. The x-axis corresponds to the total number of predictors included in each model, while the y-axis corresponds to the AUC value which is a measure of goodness of fit for classification datasets. A model with a high AUC value corresponds to better classification performance than a model with a lower AUC value. Standard errors on AUC estimates are calculated from 10 rounds of 5-fold cross-validation. Indicated are the best performing and the selected models, in red and blue respectively. In some cases, there is no difference in complexity between the best and selected models.}
  \label{fig:emys_sel}
\end{figure}

\afterpage{\clearpage}
\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/emys_oos_sel}
  \caption{Comparison of out-of-sample AUC estimates from the predictions of selected models (Fig. \ref{fig:emys_sel}), grouped by classification scheme. The horizontal line in each panel corresponds to the average AUC value across all models of that classification scheme.}
  \label{fig:emys_oos}
\end{figure}

@@

\section{Discussion}

As expected, our ensemble approach yields high out-of-sample classification performance for the first two datasets. These results indicate that in cases of clear class separation (Fig. \ref{fig:other_pca}) our approach is able to detect this and make good out-of-sample prediction.

@@

\subsection{Is there more than one species of Western Pond Turtle?}

@@

\section*{Acknowledgements}
Data collection for this project was supported in part by NSF DBI-0306158 (to KDA). G. Miller assisted with data collection and her participation in this research was supported by NSF REU DBI-0353797 (to R. Mooi of CAS). For access to emydine specimens, we thank: J. Vindum and R. Drewes (CAS); A. Resetar (FMNH); R. Feeney (LACM); C. Austin (LSUMNS); S. Sweet (MSE); J.McGuire and C. Conroy (MVZ); A. Wynn (NMNH); P. Collins (SBMNH); B. Hollingsworth (SDMNH); P. Holroyd (UCMP). We are grateful for S. Sweet for field assistance and the California Department of Fish and Game for permits. We would also like to thank M. Lambruschi (FMNH) for help with figure \ref{fig:map}.

\bibliographystyle{abbrvnat}
\bibliography{turtle,packages}

>>>>

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{amsmath, amsthm}
\usepackage{graphicx,hyperref}
\usepackage{microtype, parskip}
\usepackage[font=small]{caption}
\usepackage{float}
\usepackage{subcaption, multirow, morefloats}
\usepackage{wrapfig}
\usepackage{afterpage}
\usepackage{rotating}
\usepackage{lineno}

%%%%%%%%%%%%%%%%%%%%%
% LaTeX packages
%%%%%%%%%%%%%%%%%%%%%
% Please be sparing in your use of additional LaTeX packages, and
% upload any required style files to Editorial Manager with the file
% type "LaTeX ancillary files (.sty, .bst)."

%%%%%%%%%%%%%%%%%%%%%
% Line numbering
%%%%%%%%%%%%%%%%%%%%%
\usepackage{lineno}
% Please use line numbering with your initial submission and
% subsequent revisions. After acceptance, please comment out 
% the commands \usepackage{lineno}, \linenumbers{} 
% and \modulolinenumbers[3] below.

\title{Ensemble approaches for estimating congruence between species delimitation and morphological variation: comparing taxonomic hypotheses for the Pacific Pond Turtle (\textit{Emys marmorata})}

%%%%%%%%%%%%%%%%%%%%%
% Authorship
%%%%%%%%%%%%%%%%%%%%%
% Please remove authorship information while your paper is under review,
% unless you wish to waive your anonymity under double-blind review. 
% Remember to uncomment the information after acceptance.

\author{Peter D Smits$^{1,\ast,\dag}$ \\ 
Kenneth D Angielczyk$^{2}$ \\ 
Bryan L Stuart$^{3}$ \\
James F Parham$^{4}$}

\date{}

\begin{document}
% The journal does not have numbered sections in the main portion of
% articles. Please refrain from using section references such as
% section~\ref{section:CountingOwlEggs}, and refer to sections by name
% (e.g. section ``Counting Owl Eggs'').

% Please note that we prefer (\citealt{Xiao2015}) to \citep{Xiao2015},
% since \citep{} inserts a comma after "et al."

\maketitle

\noindent{}1. Department of Integrative Biology, University of California -- Berkeley, Berkeley, CA, USA;

\noindent{}2. Integrative Research Center, Field Museum of Natural History, Chicago, IL, USA;

\noindent{}3. Section of Research and Collections, North Carolina Museum of Natural Sciences, Raleigh, NC, USA;

\noindent{}4. John D. Cooper Archaeological and Paleontological Center, Department of Geological Sciences, California State University Fullerton, Fullerton, CA, USA.

\noindent{}$\ast$ Corresponding author; e-mail: psmits@berkeley.edu

\noindent{}$\dag$ ORCIDs: Smits, 0000-0003-4074-1447.

\bigskip

\textit{Manuscript elements}: Figure~1, figure~2, figure~3, figure~4, figure~5, figure~6, figure~7, figure~8, figure~9, table~1, table~2, table~3. Figures 1, 3, 4, 6, 8 are in color.

\bigskip

\textit{Keywords}: Geometric morphometrics, machine learning, conservation, Testudinae.

\bigskip

\textit{Manuscript type}: Article. 
% Or e-article, note, e-note, natural history miscellany,
% e-natural history miscellany, comment, reply, symposium, or
% countdown to 150.

\bigskip

\noindent{\footnotesize Prepared using the suggested \LaTeX{} 
template for \textit{Am.\ Nat.}}

\linenumbers{}
\modulolinenumbers[3]

\newpage{}

\section*{Abstract}

  We investigated the morphometric identification of cryptic species using machine learning approaches by examining their implications for a recently proposed cryptic turtle species (\textit{Emys pallida}). We collected landmark-based morphometric data from 532 adult \textit{E. marmorata/``E. pallida''} museum specimens. We assigned a classification to each specimen for six different binning schemes based on geographic occurrence data recorded in museum collection archives. We used an ensemble of supervised machine learning approaches to determine which classification hypothesis was best supported by the data. In addition, we applied the same approach to two clear-cut examples, one consisting of eight unambiguously distinct species closely related to \textit{E. marmorata}, and the other consisting of two subspecies of \textit{Trachemys scripta}. Our results indicate that there is no clear ``best'' grouping of \textit{E. marmorata/``E. pallida''} based on plastron shape. In contrast, the analyses of the clear-cut examples produced near perfect classifications, demonstrating that the methods can recover correct results when an appropriate signal exists. Explanations for the lack of grouping in \textit{E. marmorata} include the possibility that genetic differentiation is not associated with plastron shape variation below the species level and/or that local selective pressures (e.g., from hydrological regime) overwhelm morphological differentiation. A reconsideration of the methods used to delimit \textit{``E. pallida,''} the lack of barriers to gene flow, the strong evidence for widespread admixture between lineages, and the fact that plastron shape can be used to delineate other emydine species and sub-species suggest that its lack of diagnosability most likely reflects the non-distinctiveness of this proposed taxon.

\newpage{}

\section*{Introduction}

Molecular systematics has repeatedly demonstrated the existence of cryptic species that can only be diagnosed using genetic data \citep{Stuart2006,Bickford2007,SchlickSteiner2007,Pfenninger2007,Clare2011,Funk2012}. In attempts to streamline the documentation of biodiversity, several methods of species delimitation that rely almost entirely on genetic data have recently been proposed \citep{Pons2006,Carstens2010,Hausdorf2010,O'Meara2010,Yang2010b,Huelsenbeck2011b}. Although strong caveats on the utility of these methods have been raised \citep{Bauer2000,Carstens2013}, they are nevertheless being used to name species \citep{Leache2010,Spinks2014}.

@@

% past work on automatic taxon identification and older approaches to classifying taxa
% why use machine learning methods
\subsection*{Background and study system}
Machine learning is an extension of known statistical methodology \citep{Hastie2009} that emphasizes predictive accuracy and generality often at the expense of the interpretability of individual parameters. Basic statistical approaches are supplemented by randomization, sorting, and partitioning algorithms, along with the maximization or minimization of summary statistics, in order to best estimate a general model for all data, both sampled and unsampled \citep{Hastie2009}. Machine learning approaches have found use in medical research, epidemiology, economics, and automated identification of images such as handwritten zip codes \citep{Hastie2009}. % additional/more specific CITATIONS?

@@

\section*{Methods}
\subsection*{Specimens, sampling, morphometrics}

@@

@@

\subsection*{Biasing effects}
% digitization
We estimated the possible effect of digitization error \citep{Arnqvist1998,Cramon2007,Munoz-MunozF.2010} on our results by comparing within-specimen (replicated) Procrustes distances to the distances between classification scheme centroids. Ten randomly-selected \textit{E. marmorata} specimens were each digitized four times, with the original set of digitized coordinates serving as a fifth replicate. These 50 landmark configurations were then Procrustes superimposed. A range of four Procrustes distances was then calculated as the average of the pairwise distances between each of the replicate configurations of a given specimen.

@@

\subsection*{Supervised learning approaches}

@@

\section*{Results}

\subsection*{Geometric morphometrics}

@@

@@

@@

\subsection*{Supervised learning}

@@

@@

\section*{Discussion}
As expected, our ensemble approach yields high out-of-sample classification performance for the first two datasets. These results indicate that in cases of clear class separation (Fig. \ref{fig:other_pca}) our approach is able to detect this and make good out-of-sample prediction.

@@

\subsection*{Is there more than one species of Western Pond Turtle?}

@@

%\section*{Conclusion}

%%%%%%%%%%%%%%%%%%%%%
% Acknowledgments
%%%%%%%%%%%%%%%%%%%%%
% You are encouraged to remove the Acknowledgments section while
% your paper is under review (unless you wish to waive your anonymity
% under double-blind review) if the Acknowledgments reveal your
% identity. If you remove this section, you will need to add it back
% in to your final files after acceptance.

%\section*{Acknowledgments}
%Data collection for this project was supported in part by NSF DBI-0306158 (to KDA). G. Miller assisted with data collection and her participation in this research was supported by NSF REU DBI-0353797 (to R. Mooi of CAS). For access to emydine specimens, we thank: J. Vindum and R. Drewes (CAS); A. Resetar (FMNH); R. Feeney (LACM); C. Austin (LSUMNS); S. Sweet (MSE); J.McGuire and C. Conroy (MVZ); A. Wynn (NMNH); P. Collins (SBMNH); B. Hollingsworth (SDMNH); P. Holroyd (UCMP). We are grateful for S. Sweet for field assistance and the California Department of Fish and Game for permits. We would also like to thank M. Lambruschi (FMNH) for help with figure \ref{fig:map}.

\newpage{}

%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%
% You can either type your references following the examples below, or
% compile your BiBTeX database and paste the contents of your .bbl file
% here. The amnatnat.bst style file should work for this---but please
% email the journal office at amnat at uchicago dot edu if you run into
% any hitches with it!
% The list below includes sample journal articles, book chapters, and
% Dryad references.

%\bibliographystyle{amnatnat}
%\bibliography{turtle,packages}
\begin{thebibliography}{86}
\providecommand{\natexlab}[1]{#1}

\bibitem[{Angielczyk and Feldman(2013)}]{Angielczyk2013a}
Angielczyk, K.~D., and C.~R. Feldman. 2013.
\newblock {Are diminutive turtles miniaturized? The ontogeny of plastron shape
  in emydine turtles}.
\newblock Biological Journal of the Linnean Society 108:727--755.

\bibitem[{Angielczyk et~al.(2011)Angielczyk, Feldman, and
  Miller}]{Angielczyk2011}
Angielczyk, K.~D., C.~R. Feldman, and G.~R. Miller. 2011.
\newblock {Adaptive evolution of plastron shape in emydine turtles.}
\newblock Evolution 65:377--394.

\bibitem[{Angielczyk and Sheets(2007)}]{Angielczyk2007}
Angielczyk, K.~D., and H.~D. Sheets. 2007.
\newblock {Investigation of simulated tectonic deformation in fossils using
  geometric morphometrics}.
\newblock Paleobiology 33:125--148.

\bibitem[{Arnqvist and M{\aa}rtensson(1998)}]{Arnqvist1998}
Arnqvist, G., and T.~M{\aa}rtensson. 1998.
\newblock {Measurement error in geometric morphometrics: Empirical strategies
  to assess and reduce its impact on measures of shape}.

\bibitem[{Baird and Girard(1852)}]{Baird1852}
Baird, S.~F., and C.~Girard. 1852.
\newblock {Descriptions of new species of reptiles collected by the U.S.
  Exploring Expedition under the command of Capt. Charles Wilkes}.
\newblock Proceedings of the National Academy of Sciences Philadelphia
  6:174--177.

\bibitem[{Bauer et~al.(2000)Bauer, Parham, Brown, Stuart, Grismer, Papenfuss,
  Bohme, Savage, Carranza, Grismer, Wagner, Schmitz, Ananjeva, and
  Inger}]{Bauer2000}
Bauer, A.~M., J.~F. Parham, R.~M. Brown, B.~L. Stuart, L.~Grismer, T.~J.
  Papenfuss, W.~Bohme, J.~M. Savage, S.~Carranza, J.~L. Grismer, P.~Wagner,
  A.~Schmitz, N.~B. Ananjeva, and R.~F. Inger. 2000.
\newblock {Availability of new Baysian-delimited gecko names and the importance
  of character-based species descriptions}.
\newblock Proceedings of the Royal Society B: Biological Sciences 278:490--492.

\bibitem[{Baylac et~al.(2003)Baylac, Villemant, and Simbolotti}]{Baylac2003}
Baylac, M., C.~Villemant, and G.~Simbolotti. 2003.
\newblock {Combining geometric morphometrics with pattern recognition for the
  investigation of species complexes}.
\newblock Biological Journal of the Linnean Society 80:89--98.

\bibitem[{Bickford et~al.(2007)Bickford, Lohman, Sodhi, Ng, Meier, Winker,
  Ingram, and Das}]{Bickford2007}
Bickford, D., D.~J. Lohman, N.~S. Sodhi, P.~K.~L. Ng, R.~Meier, K.~Winker,
  K.~K. Ingram, and I.~Das. 2007.
\newblock {Cryptic species as a window on diversity and conservation.}
\newblock Trends in ecology {\&} evolution 22:148--55.

\bibitem[{Breiman et~al.(1984)Breiman, Friedman, Stone, and
  Olshen}]{Breiman1984}
Breiman, L., J.~Friedman, C.~J. Stone, and R.~A. Olshen. 1984.
\newblock {Classification and regression trees}.
\newblock Wadsworth International Group, Belmont.

\bibitem[{Bury(2017)}]{Bury2017}
Bury, R.~B. 2017.
\newblock {Biogeography of Western Pond Turtles in the western Great Basin:
  Dispersal Across a Northwest Passage ?}
\newblock Western Wildlife2 4:72--80.

\bibitem[{Bury et~al.(2010)Bury, Germano, and Bury}]{Bury2010}
Bury, R.~B., D.~J. Germano, and G.~W. Bury. 2010.
\newblock {Population Structure and Growth of the Turtle Actinemys marmorata
  from the Klamath–Siskiyou Ecoregion: Age, Not Size, Matters}.
\newblock Copeia 2010:443--451.

\bibitem[{Buskirk et~al.(2005)Buskirk, Parham, and Feldman}]{Buskirk2005}
Buskirk, S.~W., J.~F. Parham, and C.~R. Feldman. 2005.
\newblock {On the hybridisation between two distantly related Asian turtles
  (Testudines: Scalia x Mauremys)}.
\newblock Salamandra 41:21--26.

\bibitem[{Cardini et~al.(2009)Cardini, Nagorsen, O'Higgins, Polly, {Thorington
  Jr}, and Tongiorgi}]{Cardini2009a}
Cardini, A., D.~Nagorsen, P.~O'Higgins, P.~D. Polly, R.~W. {Thorington Jr}, and
  P.~Tongiorgi. 2009.
\newblock {Detecting biological distinctiveness using geometric morphometrics:
  an example case from the Vancouver Island marmot}.
\newblock Ethology Ecology {\&} Evolution 21:209--223.

\bibitem[{Carstens and Dewey(2010)}]{Carstens2010}
Carstens, B.~C., and T.~A. Dewey. 2010.
\newblock {Species Delimitation Using a Combined Coalescent and
  Information-Theoretic Approach: An Example from North American Myotis Bats}.
\newblock Systematic Biology 59:400--414.

\bibitem[{Carstens et~al.(2013)Carstens, Pelletier, Reid, and
  Satler}]{Carstens2013}
Carstens, B.~C., T.~a. Pelletier, N.~M. Reid, and J.~D. Satler. 2013.
\newblock {How to fail at species delimitation.}
\newblock Molecular ecology 22:4369--83.

\bibitem[{Caumul and Polly(2005)}]{Caumul2005a}
Caumul, R., and P.~D. Polly. 2005.
\newblock {Phylogenetic and environmental components of morphological
  variation: skull, mandible, and molar shape in marmots (Marmota, Rodentia).}
\newblock Evolution; international journal of organic evolution 59:2460--72.

\bibitem[{Clare(2011)}]{Clare2011}
Clare, E.~L. 2011.
\newblock {Cryptic species? Patterns of maternal and paternal gene flow in
  eight neotropical bats.}
\newblock PloS one 6:e21460.

\bibitem[{Claude(2006)}]{Claude2006}
Claude, J. 2006.
\newblock {Convergence induced by plastral kinesis and geometric morphometric
  assessment: a geometric morphometric assessment}.
\newblock Fossil Turtle Research 1:34--45.

\bibitem[{Claude et~al.(2003)Claude, Paradis, Tong, and Auffray}]{Claude2003a}
Claude, J., E.~Paradis, H.~Tong, and J.~C. Auffray. 2003.
\newblock {A geometric morphometric assessment of the effects
  of$\backslash$nenvironment and cladogenesis on the evolution of
  the$\backslash$nturtle shell}.
\newblock Biological Journal of the Linnean Society 79:485--501.

\bibitem[{Dayrat(2005)}]{Dayrat2005a}
Dayrat, B. 2005.
\newblock {Towards integrative taxonomy}.
\newblock Biological Journal of the Linnean Society 85:407--415.

\bibitem[{{De Queiroz}(2007)}]{DeQueiroz2007b}
{De Queiroz}, K. 2007.
\newblock {Species concepts and species delimitation.}
\newblock Systematic Biology 56:879--86.

\bibitem[{Demandt and Bergek(2009)}]{Demandt2009}
Demandt, M.~H., and S.~Bergek. 2009.
\newblock {Identification of cyprinid hybrids by using geometric morphometrics
  and microsatellites}.
\newblock Journal of Applied Ichthyology 25:695--701.

\bibitem[{Dillard(2017)}]{Dillard2017}
Dillard, K.~C. 2017.
\newblock {A comparative analysis of geometric morphometrics across two
  Pseudemys turtle species in east central Virginia}.
\newblock Masters.
\newblock Virginia Commonwealth University.

\bibitem[{Dobigny et~al.(2003)Dobigny, Granjon, Aniskin, Ba, and
  Voloboulev}]{Dobigny2003}
Dobigny, G., L.~Granjon, V.~Aniskin, K.~Ba, and V.~Voloboulev. 2003.
\newblock {A new sigling species of Taterillus (Muridae, Gerbillinae) from West
  Agrica}.
\newblock Mammalian Biology 68:299--316.

\bibitem[{Dryden(2013)}]{Dryden2013}
Dryden, I.~L. 2013.
\newblock shapes: Statistical shape analysis.
\newblock R package version 1.1-8.

\bibitem[{Dryden and Mardia(1998)}]{Dryden1998a}
Dryden, I.~L., and K.~Y. Mardia. 1998.
\newblock {Statistical shape analysis}.
\newblock Wiley, New York.

\bibitem[{Edwards et~al.(2011)Edwards, Claude, {Van Vuuren}, and
  Matthee}]{Edwards2011}
Edwards, S., J.~Claude, B.~J. {Van Vuuren}, and C.~A. Matthee. 2011.
\newblock {Evolutionary history of the Karoo bush rat, Myotomys unisulcatus
  (Rodentia: Muridae): Disconcordance between morphology and genetics}.
\newblock Biological Journal of the Linnean Society 102:510--526.

\bibitem[{Eldredge and Gould(1972)}]{Eldredge1972}
Eldredge, N., and S.~J. Gould. 1972.
\newblock {Punctuated equilibria: an alternative to phyletic gradualism}.
\newblock Pages 82--115 \emph{in} T.~J.~M. Schopf, ed. Models in Paleobiology.
  Freeman Cooper, San Francisco.

\bibitem[{Feldman and Parham(2002)}]{Feldman2002}
Feldman, C.~R., and J.~F. Parham. 2002.
\newblock {Molecular phylogenetics of emydine turtles: taxonomic revision and
  the evolution of shell kinesis.}
\newblock Molecular Phylogenetics and Evolution 22:388--98.

\bibitem[{Francoy et~al.(2009)Francoy, Silva, Nunes-Silva, Menezes, and
  Imperatriz-Fonseca}]{Francoy2009}
Francoy, T.~M., R.~A.~O. Silva, P.~Nunes-Silva, C.~Menezes, and V.~L.
  Imperatriz-Fonseca. 2009.
\newblock {Gender identification of five genera of stingless bees (Apidae,
  Meliponini) based on wing morphology}.
\newblock Genetics and molecular research 8:207--214.

\bibitem[{Fruciano et~al.(2016)Fruciano, Franchini, Raffini, Fan, and
  Meyer}]{Fruciano2016}
Fruciano, C., P.~Franchini, F.~Raffini, S.~Fan, and A.~Meyer. 2016.
\newblock {Are sympatrically speciating Midas cichlid fish special? Patterns of
  morphological and genetic variation in the closely related species
  Archocentrus centrarchus}.
\newblock Ecology and Evolution 6:4102--4114.

\bibitem[{Funk et~al.(2012)Funk, Caminer, and Ron}]{Funk2012}
Funk, W.~C., M.~Caminer, and S.~R. Ron. 2012.
\newblock {High levels of cryptic species diversity uncovered in Amazonian
  frogs.}
\newblock Proceedings of the Royal Society B: Biological Sciences 279:1806--14.
